\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-05-28 write_up/mixfishsim_ecolmod.tex
Correct temporal plot

For the closures based on 'real population' (bottom row), the most
disaggregated data (a weekly timescale and 1 x 1 resolution) was most
effective, reducing fishing mortality on species 1 (left) by $\sim$ 60 \%. Next
was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
yearly closures (blue lines) at all spatial resolutions, which resulted in
increased fishing mortalities ($>$ 30 \% - \textcolor{blue}{N.B. Note though,
	this is consistent with the increasing trends in F, which is probably
	more related to the fact that Fs hadn't stabilised in the simulation
	from the fishing vessels "learning" the best locations - I will rerun
	the sims for a longer time (20 - 30 years)}. \\

>>>>

For the closures based on 'real population' (bottom row), the most
disaggregated data (a weekly timescale and 1 x 1 resolution) was most
effective, reducing fishing mortality on species 1 (left) by $\sim$ 60 \%. Next
was the monthly closures ($<$ $\sim$ 30 \%).  The least effective were the
yearly closures (blue lines) at all spatial resolutions, which resulted in
increased fishing mortalities ($>$ 30 \%). \\
